# Installation {#installation}

**scMINER2 INSTALLATION INSTRUCTIONS:**

The **scMINER2** package can be installed from [Github](https://github.com/jyyulab/scMINER2):

```{r eval=FALSE}
install.packages("devtools")
devtools::install_github("jyyulab/scMINER2", dependencies = T)
```

Other dependencies for **scMINER2** can be installed following the instructions below:

1. Create a conda environment for homer using prebuild environment file provided with **scMINER2** R package. 

```{r eval=FALSE}
# In R, run to get path of homer.yml file.
system.file("extdata", "homer.yml", package = "scMINER2")
``` 

```{bash, eval=FALSE, engine.opts = list(highlight = TRUE)}
# Create a conda environment for homer
conda env create --name homer_env --file=homer.yml
conda activate homer_env

# Install hg38 and mm10 genome using the example below:
perl /home/ydhungan/.conda/envs/homer_env/share/homer/.//configureHomer.pl -install hg38
perl /home/ydhungan/.conda/envs/homer_env/share/homer/.//configureHomer.pl -install mm10
```
\
2. Install bwtool system-wide following the [bwtool](https://github.com/CRG-Barcelona/bwtool/wiki) tutorial. 
For local installation of **bwtool** follow the steps below:

```{bash, eval=FALSE, engine.opts = list(highlight = TRUE)}
# Install a local copy of the bwtool
git clone 'https://github.com/CRG-Barcelona/bwtool'
git clone 'https://github.com/CRG-Barcelona/libbeato'
git clone 'https://github.com/madler/zlib'
cd libbeato/
git checkout 0c30432af9c7e1e09ba065ad3b2bc042baa54dc2
./configure
make
cd ..
cd zlib
./configure
make
cd ..
cd bwtool/
./configure CFLAGS='-I../libbeato -I../zlib' LDFLAGS='-L../libbeato/jkweb -L../libbeato/beato -L../zlib'
make
# copy or move the binary to PATH or to a directory under PATH
sudo cp bwtool /usr/local/bin 
```
\
3. Create a conda environment for cNMF using prebuild environment file provided with **scMINER2** R package. 
```{r eval=FALSE}
# In R, run to get path of cnmf.yml file
system.file("extdata", "cnmf.yml", package = "scMINER2")
```

```{bash, eval=FALSE, engine.opts = list(highlight = TRUE)}
# Create a conda environment for cNMF
conda env create --name cnmf_env --file=cnmf.yml
```

You can write citations, too. For example, we are using the **bookdown** package [@R-bookdown] in this sample book, which was built on top of R Markdown and **knitr** [@xie2015].
